Analysis of the inference of ratings and rankings on Higher Order Networks with complex topologies

### 2025-09-03 draft/draft.tex
progress

>>>>

To define HodgeRank, it is convenient to introduce a simplicial complex composed of a 0-simplex $i$ for each team, a 1-simplex $ij$ for each pairwise comparison $\psi_{ij}$ between teams and a 2-simplex $ijk$ for each existing triple $(ij,jk,ki)$ in the set of 1-simplices.
Recall here that $ij$ and $ji$ are both labels of the same simplex, as well as any permutation of $ijk$ is also a label of the same 2-simplex.
